\section{Introduction}
\label{sec:introduction}

Game theory has long been a stable consumer of formal-mathematical
notation, but its primary objects — strategy spaces, equilibria,
mechanisms — are presented in textbooks~\citep{OsborneRubinstein1994,
MaschlerSolanZamir2013, ShohamLeytonBrown2008, Myerson1991} in a
mixture of styles that resists direct mechanization.  A
mechanization must commit, line by line, to whether ``a game'' means
a tree, a payoff matrix, an information-set diagram, a stochastic
process, or a Bayesian belief structure; whether ``a strategy'' is a
function on histories, on information sets, or on observation
sequences; whether ``probability'' lives in the discrete or the
measure-theoretic world; and whether ``equilibrium'' is a predicate
on a single profile, a profile distribution, or a correlation
device.  The textbook style routinely picks the most convenient
answer locally, then quietly switches when the next theorem
benefits from a different one.

This paper presents a Lean~4 library that picks one answer at the
bottom and pays the cost of plumbing every other notion through it.
At the bottom is a discrete-probability, utility-aware object — the
\emph{kernel game}.  Every other representation in the library —
normal-form, extensive-form, multi-agent influence diagrams,
multi-round games, factored-observation stochastic games, and
intrinsic-form games — is a \emph{language} whose semantics is a
kernel game.  Solution concepts are defined once on the kernel-game
(and game-form) layer and inherited by every language.  Theorems
about specific representations are stated either as theorems about
their kernel games or as theorems about commuting compilations
between languages.

\subsection{Contributions}

\begin{enumerate}[leftmargin=*]

\item \emph{A semantic core that is small enough to share.}  The
\TT{KernelGame} record (\Cref{sec:semantic-core}) and its
utility-free shadow \TT{GameForm} are tiny:\ a strategy family, an
outcome type, a stochastic kernel, and (for kernel games) a utility.
Solution concepts are defined as predicates on this carrier and on
\TT{GameForm}, parameterized by an arbitrary preference relation on
outcome distributions.  Every representation downstream — and every
external consumer of the library — works against the same predicate
schema.

\item \emph{A protocol/preference split that pays for itself.}
Following classical mechanism-design practice~\citep{Myerson1991},
we make the split between protocol and preferences structural:
\TT{GameForm} carries the strategy-and-outcome structure, while
\TT{KernelGame} adjoins utility.  The preference-parameterized
\TT{*For} predicates let structural theorems live below expected
utility, with the EU-specific predicates recovered as wrappers
(\Cref{sec:semantic-core:for-style}).

\item \emph{Languages and bridges as commuting compilations.}  Each
language layer (NFG, EFG, MAID, MultiRound, FOSG, Intrinsic) ships with
syntax, an SOS-style operational semantics, and a denotational
\TT{toKernelGame} that is the official semantic anchor.  Bridges
between languages are not merely translations between syntactic
objects but theorems that two compilation paths to the same kernel
game agree.  This is what lets, for example, an EFG strategy theorem
be transported to a MAID by composing two bridges, without
re-proving anything strategic.  Richer bridges may also add traces or
change the strategy representation; in those cases the theorem carries
an explicit deviation-transport condition.  Informally, deviations
after translation have to be matched before translation with the same
observable behavior.

\item \emph{A flagship theorem layer.}  The mechanized theorem suite
includes mixed Nash existence via Brouwer on the product simplex,
correlated and coarse-correlated equilibrium existence, no-regret
routes to $\varepsilon$-CCE, von Neumann minimax, an observable
mixed-action approximate discounted folk theorem, Zermelo's backward
induction, the one-shot deviation principle, Kuhn's behavioral/mixed
equivalence, Shapley-value uniqueness, and Gale--Shapley stable
matching.  Each theorem is stated on the appropriate semantic layer:
some live directly on \TT{KernelGame} / \TT{GameForm}; others, such
as Kuhn's theorem and extensive-form backward induction, live on the
observation-model or EFG substrate and are exported through the
language compilers.

\item \emph{An expressiveness layer.}  Beyond raw compilation, the
library exposes a \emph{relation-parameterized expressiveness
framework}:\ a comparison between two languages is a translation
on syntax paired with a soundness theorem stating that the
compiled kernel games agree under a chosen relation $R$
(protocol equivalence, utility-distribution equivalence, EU-equivalence, refinement, etc.;
\Cref{sec:languages:expressiveness}).  This is what gives
substantive content to claims like ``every bounded MAID is an EFG
up to utility-distribution equivalence,'' which is mechanized as an
$R$-reduction in this framework.  The companion ``every finite NFG is
a one-shot FOSG'' is exposed at the kernel-morphism layer as
\TT{NFGGame.toFOSG\_morphism}, rather than as an
\TT{Expressiveness} reduction.  Comparisons outside the library's
formalized bridge set (e.g., MAID directly to multi-round) appear as
targets in \Cref{sec:future}.

\item \emph{Mechanism-design, social-choice, and auction consumers.}
Bayesian games, finite information-design primitives, a finite
revelation principle, social-choice machinery, contract-theory
examples, and auction fragments (Vickrey, first-price, all-pay, VCG)
are formalized as consumers of the library.  The consumer layer
includes Arrow, Gibbard--Satterthwaite, Sen's liberal paradox,
Vickrey and VCG dominant-strategy truthfulness, first-price
no-dominant-strategy results, and format-specific all-pay payoff
lemmas.
\end{enumerate}

\subsection{What this library is not}

It is not a measure-theoretic foundation.  All probability is
discrete, encoded by mathlib's \TT{PMF}~\citep{mathlib2020} (we
explain in \Cref{sec:preliminaries} what is gained and lost by this
choice).  It is not a computational engine:\ many definitions are
\TT{noncomputable}, depending on classical choice for irrelevant
case splits, and we are explicit about where a constructive
implementation would diverge.  It is not a coverage of continuous
games:\ the theorem layer works under finite carrier hypotheses, and
the core expectation operator reduces to finite sums in those cases.
It is, finally, not a stand-alone proof assistant for
game-theoretic claims:\ it is a mechanized library, designed to be
imported, depended on, and extended.

\subsection{The cooperative branch}

The library's main content is \emph{non-cooperative} game theory
— strategies, best responses, equilibria, and the language layer
that compiles into kernel games.  The \emph{cooperative}
tradition (TU coalitional games, axiomatic bargaining, two-sided
matching) is collected in a parallel \TT{Cooperative/} branch:\
its primitives are coalition value functions, feasible payoff
sets, or preference rankings rather than per-player strategies,
and it does not go through \TT{KernelGame}.  The two branches
share the player-index type and $\RR$ but no load-bearing
abstractions; they live in the same package only for packaging
convenience.  We state two representative major theorems from this
branch in the paper: Shapley value uniqueness
(\Cref{thm:shapley-unique}) and Gale--Shapley stable matching
(\Cref{thm:gale-shapley}).  The remaining cooperative material is
summarized with the extension targets in
\Cref{sec:future:cooperative}.

\subsection{Reading guide}

The \emph{Definitional Supplement} is the declaration-level reference
for the paper.  It records the Lean signatures of the major objects
and theorems together with textbook correspondences, so a reader who
wants to verify that ``what the library calls Nash equilibrium is the
textbook Nash equilibrium'' can do so by inspection.  The paper gives
the narrative and proof structure; the supplement gives the
faithfulness certificate.  Cross-references below point to the
relevant supplement sections.

\Cref{sec:preliminaries} fixes the probabilistic and finiteness
discipline and explains why we made the design choices we made.
\Cref{sec:semantic-core} introduces \TT{GameForm}, \TT{KernelGame},
their morphisms, and the deviation-family schema that all
equilibrium notions instantiate.  \Cref{sec:solution-concepts}
catalogues the solution concepts.  \Cref{sec:languages} introduces
the language layer and its bridges.  \Cref{sec:theorems} states the
major theorems and sketches their structure.
\Cref{sec:mechanism-auctions} covers mechanism design and auctions.
\Cref{sec:math-layer} explains the project-local \TT{Math/} layer
used by the semantic core and theorem proofs.
\Cref{sec:discussion} collects the design tradeoffs we made
explicit.  \Cref{sec:related-work} situates the library against
prior formalization efforts and against the textbook tradition.
\Cref{sec:future} lists the natural extensions.
