\section{Solution concepts}
\label{sec:solution-concepts}

This section catalogues the solution concepts the library
formalizes.  All of them sit on top of \TT{KernelGame} or
\TT{GameForm}; concrete language layers (\Cref{sec:languages})
inherit them via $\toKG$.  The presentation is grouped by the
\emph{deviation family} the concept quantifies over, which is the
underlying organizing principle of the library and makes
several otherwise-disparate equivalences (correlated $\Rightarrow$
coarse correlated, dominance $\Rightarrow$ Nash, etc.) visible as
instances of one schema.

\subsection{The deviation-family schema}
\label{sec:solution-concepts:family}

Fix a game form $\GF$, a player $i$, and a status-quo profile
distribution $\mu \in \PMF{\prod_j \Strat_j}$.  Let
$\Pref$ be a per-player weak preference on $\PMF{\Outcome}$ and
let $\mathcal{D}_i = (D_i, \mathrm{deviate}_i)$ be a
\emph{deviation family} for $i$:\ a type $D_i$ of deviations and a
function $\mathrm{deviate}_i : \PMF{\prod_j \Strat_j} \to D_i \to
\PMF{\prod_j \Strat_j}$.  A profile distribution $\mu$ is
\emph{$\mathcal{D}$-equilibrium for $\Pref$} if no player has a
profitable deviation in $\mathcal{D}$:
\begin{equation}
\label{eq:devschema}
  \forall i,\, \forall d \in D_i.\quad
    \Pref_i\;\bigl(\GF.\mathrm{correlatedOutcome}(\mu),\;
                   \GF.\mathrm{correlatedOutcome}(\mathrm{deviate}_i(\mu, d))\bigr).
\end{equation}
The library identifies exactly two deviation families that matter
for the standard solution-concept inventory:

\begin{itemize}\itemsep2pt
\item $\mathcal{D}^{\mathrm{const}}$:\ $D_i = \Strat_i$, with
$\mathrm{deviate}_i(\mu, s')$ replacing $i$'s coordinate by $s'$
on every sample of $\mu$.

\item $\mathcal{D}^{\mathrm{dep}}$:\ $D_i = \Strat_i \to \Strat_i$,
with $\mathrm{deviate}_i(\mu, \mathrm{dev})$ replacing $i$'s
coordinate $s$ by $\mathrm{dev}(s)$ on every sample.
\end{itemize}

The four ``profile-distribution'' equilibria of the library are
then schema instances:
\[
  \begin{array}{lcl}
    \IsNashFor(\Profile)
      &\equiv& \mathcal{D}^{\mathrm{const}}\text{-eq for } \Dirac_\Profile, \\
    \IsCoarseCorrelatedEqFor(\mu)
      &\equiv& \mathcal{D}^{\mathrm{const}}\text{-eq for } \mu, \\
    \IsCorrelatedEqFor(\mu)
      &\equiv& \mathcal{D}^{\mathrm{dep}}\text{-eq for } \mu.
  \end{array}
\]
Several library-wide consequences follow:
\begin{itemize}
\item \emph{Hierarchy}.  $\mathcal{D}^{\mathrm{const}}$ embeds into
$\mathcal{D}^{\mathrm{dep}}$ via constant deviation functions, so
every $\Pref$-CE is a $\Pref$-CCE.  Setting $\mu = \Dirac_\Profile$
recovers $\Pref$-Nash from $\Pref$-CCE.  Thus pure Nash point masses
are CCEs, and CE distributions are CCE distributions; CE and CCE are
both predicates on profile distributions, while Nash is a predicate
on point profiles.
\item \emph{Monotonicity in $\Pref$}.  If $\Pref^{(2)}$ implies
$\Pref^{(1)}$ pointwise, then any $\mathcal{D}$-equilibrium for
$\Pref^{(2)}$ is a $\mathcal{D}$-equilibrium for $\Pref^{(1)}$.
The library exposes this as
\TT{IsNashFor.mono} and \TT{IsDominantFor.mono}.
\item \emph{Transport across presentations}.  Because the schema is
phrased in terms of the outcome distribution before and after an
allowed deviation, it admits a representation-independent transport
principle: if two presentations have the same observed status-quo
law and every allowed deviation in the target presentation is
matched by an allowed deviation in the source presentation with the
same observed law, then equilibrium transfers from source to target.
The Nash transport theorem is the point-mass,
$\mathcal{D}^{\mathrm{const}}$ instance; CE and CCE use the same
statement at the profile-distribution level.
\end{itemize}

\leancorr{Schema in \TT{Concepts/Equilibrium/GameFormSolutionConcepts.lean};
transport in \TT{Concepts/Foundations/DeviationSimulation.lean}; full Lean text
in supplement~§3.1 and §3.2.}

\subsection{Nash equilibrium and best response}
\label{sec:solution-concepts:nash}

The EU-specific Nash predicate is
\begin{equation}
\label{eq:nash}
  \IsNash_\KG(\Profile) \;\Longleftrightarrow\;
    \forall i,\, \forall s' \in \Strat_i,\;
    \EU(\KG, \Profile, i) \;\ge\; \EU(\KG, \Profile[i \mapsto s'], i),
\end{equation}
and the preference-parameterized variant on $\GF$ is the schema
instance with $\mu = \Dirac_\Profile$ and $\mathcal{D} =
\mathcal{D}^{\mathrm{const}}$.  A \emph{best response} is a
strategy that maximizes the expected utility against fixed
opponents:
\begin{equation}
\label{eq:br}
  \IsBR_\KG(i, \Profile, s) \;\Longleftrightarrow\;
    \forall s' \in \Strat_i,\;
    \EU(\KG, \Profile[i \mapsto s], i) \;\ge\;
    \EU(\KG, \Profile[i \mapsto s'], i),
\end{equation}
and the standard equivalence
\[
  \IsNash_\KG(\Profile) \;\Longleftrightarrow\;
    \forall i,\, \IsBR_\KG(i, \Profile, \Profile_i)
\]
holds at the $\GF.\IsNashFor$/$\IsBRfor$ level for any
preference and is propagated to the EU level by the bridge of
\Cref{sec:semantic-core:for-style}.

A \emph{strict Nash equilibrium} requires the inequality to be
strict for every $s' \neq \Profile_i$.  The library's
\TT{StrictNashProperties.lean} records the implication strict
$\Rightarrow$ Nash, asymmetry under a strict preference that is
incompatible with reverse weak preference, and uniqueness in
ordinal-potential games.

\paragraph{Strong Nash equilibrium.}\
A \emph{strong Nash equilibrium}~\citep{Aumann1959} strengthens
the deviation menu from singleton (unilateral) deviations to
arbitrary coalitions:\ a profile $\Profile$ is strong Nash when no
coalition $C \subseteq \Players$ has a joint deviation $\tau$ that
weakly improves every member of $C$ and strictly improves at
least one.  The library encodes the coalitional deviation as
$\mathrm{coalitionDeviation}(C, \Profile, \tau)_i =
\tau_i\ \text{if}\ i \in C,\ \Profile_i\ \text{otherwise}$, and
for the display below we abbreviate
\[
  \EU_C(i) \coloneqq
    \EU\bigl(\KG, \mathrm{coalitionDeviation}(C,\Profile,\tau), i\bigr),
  \qquad
  \EU_\Profile(i) \coloneqq \EU(\KG,\Profile,i).
\]
The predicate unfolds to
\[
  \IsStrongNash(\Profile) \;\Longleftrightarrow\;
    \neg \exists C, \tau.\;
    (\forall i \in C, \EU_C(i) \ge \EU_\Profile(i)) \land
    (\exists i \in C, \EU_C(i) > \EU_\Profile(i))
\]
Specializing $C$ to a singleton recovers Nash, and specializing $C$
to the grand coalition $\Players$ recovers
Pareto efficiency (\Cref{sec:solution-concepts:welfare}):\ strong
Nash $\Rightarrow$ Nash $\land$ Pareto efficient.

\leancorr{\TT{Concepts/Equilibrium/StrongNash.lean} (\TT{coalitionDeviation},
\TT{IsStrongNash}, \TT{IsStrongNash.isNash},
\TT{IsStrongNash.isParetoEfficient}).}

\subsection{Dominance}
\label{sec:solution-concepts:dominance}

Two notions of dominance are formalized.  \emph{Weak dominance}:
$s$ weakly dominates $t$ for player $i$ when, for every opponent
profile, $i$'s payoff under $s$ is $\Pref$-preferred to that under
$t$.  \emph{Strict dominance} replaces $\Pref$ by a strict
preference $\sPref$ (typically the strict EU comparison).

A strategy $s$ is \emph{(weakly) dominant} for $i$ when it weakly
dominates every alternative; it is \emph{strictly dominant} when
the analogous statement holds for $\sPref$.  The library exposes
these as both EU-specific (\TT{IsDominant}, \TT{IsStrictDominant})
and preference-parameterized (\TT{IsDominantFor},
\TT{IsStrictDominantFor}).  The chain
\[
  \text{strict dominant} \;\Rightarrow\; \text{weak dominant} \;\Rightarrow\;
  \text{best response} \;\Rightarrow\; \text{Nash}
\]
is recorded modularly:\ each step is one \TT{simp}-able
proposition, with no hidden EU dependence.

\subsubsection{Iterated elimination and rationalizability}

Iterated elimination of strictly dominated strategies is encoded
as a sequence $\mathrm{Survives}_n$ of decreasing predicates: round
$0$ is true of every strategy, and round $n+1$ requires that the
strategy both survived round $n$ and is not strictly dominated by a
\emph{mixed} strategy supported on round-$n$ survivors, against every
round-$n$ survivor profile.  A strategy is \emph{rationalizable}
when it survives every round.  Following Bernheim and Pearce, the
standard notion eliminates by mixed dominators — a pure strategy can
be strictly dominated by a mixed strategy even when no single pure
strategy dominates it — so the expected payoff of a mixed deviation
$p \in \PMF{\Strat_i}$ against a pure profile is
$\mathbb{E}_{a \sim p}\,\EU(\KG, \Profile[i \mapsto a], i)$.  The
pure-dominator variant ($\mathrm{SurvivesPure}$,
$\mathrm{IsPureRationalizable}$) eliminates strictly less and so
over-approximates the rationalizable set;\ it is retained as the
weaker notion.  The library proves (the mixed statements over finite
pure-strategy spaces):
\begin{itemize}
\item Survival is monotone decreasing in rounds.
\item Every Nash strategy survives every round, hence is
rationalizable:\ a best response is not strictly beaten in
expectation by any mixed deviation.
\item Every dominant strategy is rationalizable.
\item A strategy strictly dominated by a mixed strategy
($\mathrm{StrictlyDominatedByMixed}$) is never a best response, and a
rationalizable strategy is not globally mixed-dominated.
\item In a \emph{dominant-strategy solvable} game — one in which every
player has a strictly dominant strategy, a strictly stronger condition
than textbook dominance solvability — that dominant profile is the unique
Nash equilibrium.
\end{itemize}

\leancorr{Predicates and theorems in \TT{Concepts/Dominance/Rationalizability.lean}
(\TT{Survives}, \TT{IsRationalizable}, \TT{IsNash.survives},
\TT{IsNash.isRationalizable}, \TT{IsDominant.isRationalizable},
\TT{IsRationalizable.not\_globally\_dominated}; pure variants
\TT{SurvivesPure}, \TT{IsPureRationalizable}); mixed dominance in
\TT{Concepts/Dominance/DominanceSolvable.lean}
(\TT{StrictlyDominatedByMixed}, \TT{StrictlyDominatedByMixed.not\_best\_response});
dominant-strategy solvability in
\TT{Concepts/Dominance/DominanceSolvability.lean}
(\TT{IsDominantStrategySolvable}, \TT{IsDominantStrategySolvable.exists\_unique\_nash}).}

\subsection{Correlated and coarse correlated equilibria}
\label{sec:solution-concepts:correlated}

Aumann's correlated equilibrium~\citep{Aumann1974} interprets
$\mu \in \PMF{\prod_i \Strat_i}$ as a public correlation device
that samples a profile $s \sim \mu$ and privately recommends $s_i$ to
player $i$.  The
device is incentive-compatible when no player gains in expectation
by ignoring the recommendation in favor of any function of it.
This is exactly $\mathcal{D}^{\mathrm{dep}}$-equilibrium under EU.
Coarse correlated equilibrium~\citep{HartMasColell2000} weakens the
deviation menu from arbitrary functions to constant strategies,
which yields $\mathcal{D}^{\mathrm{const}}$-equilibrium under EU.

The library proves the standard inclusions
\[
  \Dirac(\Pref\text{-Nash}) \;\subseteq\; \Pref\text{-CCE},
  \qquad
  \Pref\text{-CE} \;\subseteq\; \Pref\text{-CCE}.
\]
Here \TT{IsCorrelatedEqFor.toCoarseCorrelatedEqFor} records the CE
$\Rightarrow$ CCE inclusion; the Nash-to-CCE statement is the schema
instance $\mu = \Dirac_\Profile$.  In the EU-specific layer, existence of
correlated and coarse correlated equilibria for any finite
$\KG$ is the content of \Cref{sec:theorems:correlated-existence}.

\paragraph{The welfare gain from correlation.}\
Summing equilibrium expected utilities gives the \emph{correlated
social welfare} of a device, and maximizing it over correlated
(resp.\ coarse correlated) equilibria gives the best welfare each
regime can support.  Because a pure Nash equilibrium is a CE and a CE
is a CCE, these optima form an increasing ladder — best pure-Nash
welfare $\le$ best CE welfare $\le$ best CCE welfare — and the
\emph{correlation welfare gap} is the nonnegative difference between the
ends.  The Nash benchmark is the best \emph{pure} Nash welfare, matching
the price-of-anarchy convention of
\Cref{sec:solution-concepts:welfare}.  This is the additive analogue of
the Ashlagi–Monderer–Tennenholtz \emph{value of correlation}, which is a
welfare \emph{ratio} against the best mixed Nash; the additive gap here
needs no positivity assumption.  In a team game it collapses to zero
(\TT{IsTeamGame.correlationWelfareGap\_eq\_zero}):\ with aligned
interests the welfare-optimal profile is already Nash, so correlation
buys nothing.

\leancorr{\TT{Concepts/Correlation/ValueOfCorrelation.lean}
(\TT{correlatedSocialWelfare}, \TT{bestCorrelatedWelfare},
\TT{bestCoarseCorrelatedWelfare}, \TT{correlationWelfareGap},
\TT{correlationWelfareGap\_nonneg},
\TT{IsTeamGame.correlationWelfareGap\_eq\_zero}).}

\subsection{Equilibrium payoff sets and the timing of information}
\label{sec:solution-concepts:signal-timing}

The deviation-family schema presents Nash (on point profiles, embedded
as Dirac profile distributions), correlated, and coarse correlated
equilibria as instances of one schema.  Collecting the player payoff
vectors they realize gives three \emph{equilibrium payoff sets}, nested
by the hierarchy of \Cref{sec:solution-concepts:family},
\[
  \mathrm{nashPayoffSet}(\KG)
  \;\subseteq\;
  \mathrm{correlatedPayoffSet}(\KG)
  \;\subseteq\;
  \mathrm{coarseCorrelatedPayoffSet}(\KG)
  \;\subseteq\; \Payoff{\Players}.
\]
These are the payoff-level counterpart of the welfare ladder above and
the natural objects for comparing what an equilibrium concept — or an
information structure — can achieve.

\paragraph{A finite signal-timing separation.}\
The library includes a two-player witness that these sets depend on
\emph{when} exogenous randomness is revealed, not only on its
distribution.  A fair public coin precedes a coordination game:\
player~$0$ chooses whether to \textsf{enter}, after which both players
pick a continuation action.  If both continuation actions match the
coin, entry pays $(4,3)$ on heads and $(1,3)$ on tails; opting out pays
$(2,2)$; entering and miscoordinating pays $(0,0)$.  Two kernel games
differ \emph{only} in player~$0$'s strategy type:\ in the
\emph{late-signal} game the entry decision is coin-blind (the coin is
revealed only afterwards), while in the \emph{early-signal} game
player~$0$ may condition entry on the coin.

Revealing the coin later \emph{enlarges} player~$1$'s achievable
equilibrium value.  Entering blind pools the two branches into an
ex-ante-attractive average ($\tfrac{4+1}{2} = \tfrac52 > 2$), so the
late-signal game has a Nash equilibrium of value $3$ for player~$1$.
Early revelation instead lets player~$0$ opt out in the bad branch —
individually rational, but it destroys the arrangement:\ every
early-signal Nash \emph{and} correlated equilibrium caps player~$1$ at
$\tfrac52$, attained.  Coarse correlation does strictly better yet still
cannot reach $3$:\ the early-signal coarse-correlated cap is exactly
$\tfrac{11}{4}$, also attained.  For player~$1$,
\[
  \underbrace{\tfrac52}_{\text{early Nash}}
  = \underbrace{\tfrac52}_{\text{early CE}}
  \;<\; \underbrace{\tfrac{11}{4}}_{\text{early CCE}}
  \;<\; \underbrace{3}_{\text{late Nash}},
\]
each cap tight.  The middle inequality is a genuine strictness of the
payoff-set hierarchy on a single game,
$\mathrm{correlatedPayoffSet} \subsetneq
\mathrm{coarseCorrelatedPayoffSet}$, witnessed by a coarse-correlated
device that — being open only to \emph{constant} disobedience — keeps
player~$0$ entering on the bad branch, where the
recommendation-dependent deviation available against a correlated device
would not.

This is a finite witness to a classical phenomenon:\ the value of
information is not monotone in games.  For a single decision-maker
earlier information is weakly valuable (the example includes the
one-player Blackwell comparison $3 \ge \tfrac52$
\citep{Blackwell1953}); in the two-player game the very deviation a lone
agent would use to exploit early information is what collapses the other
player's equilibrium — the Hirshleifer effect \citep{Hirshleifer1971}.
That the value of information can be \emph{negative} in games, in
contrast to the single-agent monotonicity, is the subject of a
literature characterizing when it nonetheless stays positive
\citep{Bassan2003}.  The correlated/coarse-correlated gap is the finite
normal-form shadow of the extensive-form mediated-recommendation gap
\citep{vonStengelForges2008} and of the solution-concept-dependence of
outcome equivalence of information structures
\citep{LehrerRosenbergShmaya2010, LehrerRosenbergShmaya2013}, and the
payoff-set comparison is an instance of the comparison of information
structures \citep{BergemannMorris2016}.  At the representation level the same
contrast says that swapping a chance node across a decision node — a
move that preserves the outcome law under a fixed behavioral profile —
is \emph{not} strategically inessential once it changes what the
decision observes, the boundary case of the interchange-of-moves
transformation \citep{Thompson1952, ElmesReny1994}.

\leancorr{Payoff sets in
\TT{Concepts/Equilibrium/SolutionConcepts.lean} (\TT{nashPayoffSet},
\TT{correlatedPayoffSet}, \TT{coarseCorrelatedPayoffSet}); the example,
the caps with tightness witnesses, and the separations in
\TT{Concepts/Correlation/SignalTiming.lean}
(\TT{late\_not\_covered\_by\_early\_nash},
\TT{late\_not\_covered\_by\_early\_correlated},
\TT{late\_not\_covered\_by\_early\_coarseCorrelated},
\TT{early\_coarseCorrelated\_p1\_cap},
\TT{early\_correlatedPayoffSet\_ssub\_coarse},
\TT{single\_agent\_early\_ge\_late}).}

\subsection{Pareto efficiency, social welfare, and price of anarchy}
\label{sec:solution-concepts:welfare}

A profile $\Profile$ \emph{Pareto-dominates} $\tau$ for a pair
$(\Pref, \sPref)$ when every player weakly prefers $\Profile$'s
outcome distribution and at least one player strictly does;
$\Profile$ is \emph{Pareto-efficient} when no profile dominates
it.  The EU specialization uses $\Pref^{\EU}$ and
$\sPref^{\EU}$.  The library tracks the basic structural results
— irreflexivity, asymmetry — modulo the irreflexivity and
incompatibility hypotheses on $(\Pref, \sPref)$.

\emph{Social welfare} is the EU sum
$\Welfare(\KG, \Profile) = \sum_i \EU(\KG, \Profile, i)$ over a
finite player set.  The \emph{price of anarchy}
\citep{Koutsoupias1999, Roughgarden2005} compares the
worst-case Nash welfare to the optimum,
\begin{equation}
\label{eq:poa}
  \PoA(\KG) \;=\; \frac{\sup_\Profile \Welfare(\KG, \Profile)}
                       {\inf_{\Profile \in \Nash(\KG)} \Welfare(\KG, \Profile)},
\end{equation}
with the dual \emph{price of stability}
$\sup_\Profile \Welfare / \sup_{\Profile \in \Nash} \Welfare$.
The library formalizes the welfare quantities the ratios are built
from — optimal welfare, worst Nash welfare, best Nash welfare —
the comparison lemmas between them, and the ratio-valued ratios
themselves (\TT{priceOfAnarchy}, \TT{priceOfStability}) packaged
against a nonempty-Nash hypothesis.  Both ratios are at least $1$
when the corresponding welfare denominator is positive and at
most the optimum (\TT{one\_le\_priceOfAnarchy},
\TT{one\_le\_priceOfStability}), and
$\PoS \le \PoA$ whenever the worst Nash welfare is positive
(\TT{priceOfStability\_le\_priceOfAnarchy}).  In a team game
(\Cref{sec:solution-concepts:team}), the welfare-maximizing
profile is itself Nash, so the best Nash welfare equals the
optimal welfare and $\PoS = 1$
(\TT{IsTeamGame.priceOfStability\_eq\_one}).

\paragraph{Smoothness and the robust price of anarchy.}\
The library formalizes Roughgarden's \emph{smoothness}
technique~\citep{Roughgarden2015} for bounding the price of anarchy
uniformly.  A game is \emph{$(\lambda,\mu)$-smooth} when, for any two
profiles $s, t$, the total utility from each player unilaterally
deviating toward $t$ against $s$ is at least
$\lambda\,\Welfare(t) - \mu\,\Welfare(s)$.  Smoothness at once bounds
every Nash equilibrium, $\lambda\,\Welfare(t) \le
(1+\mu)\,\Welfare(s)$ (\TT{IsSmooth.nash\_bound}), and — this is the
\emph{robust} price of anarchy — the same bound holds for every
\emph{coarse correlated equilibrium}, lifting the deviation argument
through the equilibrium distribution
(\TT{IsSmooth.coarseCorrelated\_bound}).  A single smoothness
certificate therefore caps the inefficiency not only of Nash play but
of the whole no-regret/correlated hierarchy.

\leancorr{\TT{Concepts/Welfare/Smoothness.lean}
(\TT{KernelGame.IsSmooth}, \TT{IsSmooth.nash\_bound},
\TT{IsSmooth.coarseCorrelated\_bound}).}

A small structural bridge connects welfare to Pareto efficiency:\
Pareto dominance strictly raises social welfare
(\TT{ParetoDominates.socialWelfare\_lt}); hence any
welfare-maximizing profile is Pareto-efficient
(\TT{welfareMax\_isParetoEfficient}), and a finite game
admits both a welfare-maximizing and a Pareto-efficient profile
(\TT{exists\_welfareMax}, \TT{exists\_paretoEfficient}).

\paragraph{Braess's paradox.}\
A concrete 2-player witness that adding a strategy can lower the
Nash welfare lives in \TT{Languages/NFG/Examples.lean}:\
\TT{braessRestricted} is a 2$\times$2 coordination game with two
pure Nash at welfare 6, and \TT{braessAugmented} extends both
players' action sets by a ``shortcut'' action \TT{c} that strictly
dominates the original two; the augmented game has the unique
pure Nash $(\TT{c}, \TT{c})$ with welfare 4. The companion theorem
\TT{braess\_welfare\_decreases} records the strict inequality. The
classical 4-edge network instance with congestion-dependent delays
would compile through the \TT{CongestionGame} infrastructure but
is not yet packaged.

\leancorr{Welfare quantities and ratios in
\TT{Concepts/Welfare/PriceOfAnarchy.lean}
(\TT{optimalWelfare}, \TT{worstNashWelfare}, \TT{bestNashWelfare},
\TT{priceOfAnarchy}, \TT{priceOfStability});
welfare/Pareto bridges in \TT{Concepts/Equilibrium/NashPareto.lean} and
\TT{Concepts/Welfare/WelfareTheorems.lean};
Braess instance in \TT{Languages/NFG/Examples.lean}
(\TT{braessRestricted}, \TT{braessAugmented},
\TT{braess\_welfare\_decreases}).}

\subsection{Security strategies and minimax value}
\label{sec:solution-concepts:security}

Player $i$'s \emph{security level}~\citep{vNM1944} is the
guarantee value over a worst-case opponent profile,
\begin{equation}
\label{eq:security}
  \mathrm{sec}(\KG, i) \;=\; \sup_{s \in \Strat_i}\;
    \inf_{\Profile_{-i}}\;
      \EU\bigl(\KG, (s,\Profile_{-i}), i\bigr),
\end{equation}
and a \emph{security strategy} for $i$ achieves this supremum.
The library formalizes both finite-attained versions
(\TT{worstCaseEU}, \TT{securityLevel}) and order-theoretic sup/inf
versions (\TT{worstCaseEUInf}, \TT{securityLevelSup}).  It proves
that a security strategy exists in the finite-attained case, and that
Nash payoffs are at least the corresponding security level under the
boundedness hypotheses needed for the sup/inf API.  The two-player
zero-sum theorem in
\Cref{sec:theorems:minimax} is stated through a mixed Nash profile
with saddle-style guarantee inequalities.

\leancorr{Definitions and the IR/Nash bound in
\TT{Concepts/ZeroSum/SecurityStrategy.lean} (\TT{worstCaseEU},
\TT{securityLevel}, \TT{worstCaseEUInf}, \TT{securityLevelSup});
individual-rationality interface in
\TT{Concepts/Welfare/IndividualRationality.lean}.}

\subsection{Regret}
\label{sec:solution-concepts:regret}

Internal and external regret are recorded as positive parts of
EU differences.  External regret of $\Profile$ for player $i$ is
\begin{equation}
\label{eq:regret}
  \Regret^{\mathrm{ext}}(\KG, \Profile, i) \;=\;
    \max_{s' \in \Strat_i}\,
    \bigl(\EU(\KG, \Profile[i \mapsto s'], i) - \EU(\KG, \Profile, i)\bigr)^{+};
\end{equation}
internal regret replaces the constant $s'$ by a function of
$\Profile_i$ and is the dual of the $\mathcal{D}^{\mathrm{dep}}$
deviation family that defines correlated equilibrium.  The
library proves the structural fact that a profile distribution
$\mu$ has zero average external regret iff it is a CCE, and zero
average internal regret iff it is a CE — the standard
regret-equilibrium duality~\citep{HartMasColell2000}.

\paragraph{Savage minimax regret.}\
A separate, decision-theoretic regret notion due to
\citet{Savage1951} lives in the \TT{Savage} namespace. Given a finite
action set $A$ and a finite state space $\Omega$ with utility
$u : A \times \Omega \to \RR$, the \emph{regret} of action $a$ at state
$\omega$ is $\mathrm{regret}(a, \omega) = \sup_b u(b, \omega) -
u(a, \omega)$; the \emph{maximum regret} is the worst case over states;
a \emph{minimax-regret action} minimizes the maximum regret. The
library proves that regret is non-negative, equals zero exactly at
the per-state argmaxes, and that any uniformly best action is
minimax-regret. Unlike CE/CCE regret these are properties of a
single decision-maker against Nature, not equilibrium concepts.

\leancorr{\TT{Concepts/Correlation/Regret.lean} contains the EU-regret
definitions and the \TT{Savage} namespace for minimax regret.}

\subsection{Approximate equilibria}
\label{sec:solution-concepts:approx}

An \emph{$\varepsilon$-Nash equilibrium} relaxes the Nash
inequality by an additive $\varepsilon$ slack:\ every unilateral
deviation is at most $\varepsilon$-profitable.  Closure under
$\varepsilon$-relaxation is recorded for the deviation-family
schema, so the same definition applies to $\varepsilon$-CCE and
$\varepsilon$-CE.  These approximate correlated notions carry
quantitative regret characterizations:\ a profile distribution is
an $\varepsilon$-CCE iff every player's external regret is at most
$\varepsilon$, and an $\varepsilon$-CE iff every swap regret is at
most $\varepsilon$; the exact equilibrium is the $\varepsilon=0$
instance, and the inclusion $\varepsilon$-CE $\subseteq$
$\varepsilon$-CCE lifts CE $\subseteq$ CCE to the approximate
level.  These are exactly the equilibria reached by no-regret
learning (\Cref{sec:theorems:learning}):\ the time-average of play
with cumulative regret $R$ over horizon $T$ is an
$(R/T)$-equilibrium.

\leancorr{\TT{Concepts/Equilibrium/ApproximateNash.lean} for
$\varepsilon$-Nash;\
\TT{Concepts/Correlation/ApproximateCorrelatedEq.lean} for
$\varepsilon$-CCE/$\varepsilon$-CE and their regret
characterizations (\TT{isεCoarseCorrelatedEq\_iff\_externalRegret\_le},
\TT{isεCorrelatedEq\_iff\_swapRegret\_le}).}

\subsection{Potential games}
\label{sec:solution-concepts:potential}

A function $\Pot : \prod_i \Strat_i \to \RR$ is an \emph{exact
potential}~\citep{MondererShapley1996} when, for every player $i$
and unilateral deviation $\Profile \to \Profile[i \mapsto s']$,
\begin{equation}
\label{eq:potential}
  \EU(\KG, \Profile[i \mapsto s'], i) - \EU(\KG, \Profile, i)
  \;=\;
  \Pot(\Profile[i \mapsto s']) - \Pot(\Profile);
\end{equation}
it is an \emph{ordinal potential} when the equality is replaced
by an iff between the two sides being positive.  The library
proves:
\begin{itemize}\itemsep2pt
\item Every exact potential is an ordinal potential.
\item Every (local or global) maximizer of an ordinal potential
is Nash; hence finite ordinal potential games admit pure Nash
equilibria as a direct consequence (any maximizer of $\Pot$ on
the finite product $\prod_i \Strat_i$ is Nash).
\item Best-response dynamics terminates in finitely many steps in
a finite ordinal potential game.
\item (\emph{Monderer–Shapley}) The expected (multilinear)
extension of an exact potential is an exact potential for the mixed
extension; hence the mixed extension of an exact potential game is
itself an exact potential game.  This is the reusable infrastructure
behind the fictitious-play convergence result of
\Cref{sec:theorems:learning}.
\end{itemize}
Team games (\Cref{sec:solution-concepts:team}) are an instance:\
they are exact potential games with $\Pot = u_{\mathrm{any}}$.

\leancorr{\TT{Concepts/Potential/PotentialGame.lean} (\TT{IsExactPotential},
\TT{IsOrdinalPotential}, \TT{IsExactPotential.toOrdinal},
\TT{IsOrdinalPotential.nash\_of\_maximizer});
\TT{Concepts/Potential/PotentialFIP.lean} and
\TT{Concepts/Potential/PotentialWellFounded.lean} for the dynamics;
\TT{Concepts/Potential/MixedPotential.lean} for the mixed-extension
potential (\TT{mixedPotential},
\TT{IsExactPotential.mixedExtension\_isExactPotential});
\TT{Concepts/Potential/PotentialTeam.lean} for the team-game corollary
(\TT{IsTeamGame.isExactPotential}).}

\subsection{Zero-sum, constant-sum, team, and symmetric games}
\label{sec:solution-concepts:team}

A kernel game is \emph{zero-sum} when $\sum_i \util(\omega)(i) =
0$ for every $\omega$, and \emph{constant-sum} for an
$\Outcome$-independent constant.  The library proves that the
Nash equilibria of a two-player constant-sum game give each
player guarantee inequalities against opponent deviations.

A kernel game is a \emph{team game} when all players have
identical utilities.  Team games are exact potential games with
$\Pot = \util_{\mathrm{any}}$; consequently every welfare optimum
is a Nash equilibrium, and the price of stability is $1$.

A kernel game is \emph{symmetric} when permutations of the player
type act trivially on outcome distributions and utility (modulo
the same permutation).  The library proves the structural lemmas
that permuting a Nash profile by a symmetry yields a Nash profile,
and that all players obtain equal EU at a symmetric profile.
Existence of a \emph{symmetric} mixed Nash equilibrium (i.e.\ a
fixed point of the gain map within the symmetric subspace) is a
classical corollary of mixed Nash existence~\citep{Nash1951}; the
library packages this corollary for finite symmetric games by
restricting the Nash gain map to the diagonal mixed-strategy
simplex.  \emph{Evolutionary
stability}~\citep{MaynardSmithPrice1973} is formalized as the
appropriate strict-dominance condition on a symmetric two-player
game.

\leancorr{\TT{Concepts/ZeroSum/ZeroSum.lean}, \TT{Concepts/ZeroSum/ConstantSum.lean},
\TT{Concepts/ZeroSum/ZeroSumNash.lean}, \TT{Concepts/ZeroSum/ConstantSumNash.lean},
\TT{Concepts/Classes/TeamGame.lean}, \TT{Concepts/Classes/SymmetricGame.lean}
(\TT{isSymmetricEU\_nash\_perm}, \TT{isSymmetricEU\_eu\_eq},
\TT{symmetric\_mixed\_nash\_exists}),
\TT{Concepts/Classes/EvolutionaryStability.lean}.}

\subsection{Common knowledge}
\label{sec:solution-concepts:common-knowledge}

The library also formalizes partition-based knowledge for downstream
use.  Each agent has an
\emph{information partition} $P$ of a finite state space, with
$P.\mathrm{cell}(s)$ the set of states the agent considers possible
when the true state is $s$ (reflexive at $s$; partition-coherent).
The \emph{knowledge
operator}
\[
  \Knows(P, E) \;=\; \{\,s : P.\mathrm{cell}(s) \subseteq E\,\}
\]
returns the event ``the agent knows $E$'', and the library proves
the S5 axioms it satisfies:\ veridicality $\Knows(P, E) \subseteq
E$ (T), positive introspection $\Knows(P, \Knows(P, E)) = \Knows(P,
E)$ (4), negative introspection — the complement of $\Knows(P, E)$
is itself known at every state in that complement (5) —
monotonicity in $E$, and conjunction $\Knows(P, E \cap F) =
\Knows(P, E) \cap \Knows(P, F)$.  Self-evident events are
characterized as the fixed points of $\Knows$.  Posterior
probability of $E$ given the cell at $s$ is the conditional
$\mu$-mass; the library proves Aumann's \emph{agreeing-to-disagree}
lemma~\citep{Aumann1976} that agents sharing the same cell at $s$
and the same prior $\mu$ assign the same posterior to every event,
and that the posterior on a self-evident $E$ is $1$ at every $s \in
E$ and $0$ at every $s \notin E$.

For a finite family $P_1, \dots, P_n$ of partitions,
\emph{mutual knowledge} is $\bigcap_i \Knows(P_i, E)$, and
\emph{common knowledge} of $E$ at $s$ is the existence of a
\emph{public event} $F \ni s$ with $F \subseteq E$ that is
self-evident for every $P_i$~\citep{Aumann1976}.  The library
records that common knowledge implies mutual knowledge (each
agent's $\mathrm{cell}(s)$ sits inside the public event $F$, which
in turn sits in $E$), and is itself common knowledge at the same
state (positive introspection at the group level, witnessed by the
same public event).

\paragraph{Aumann's full agreement.}\
The flagship epistemic-game-theory result built on this
infrastructure is the full-agreement theorem of \citet{Aumann1976}:
when two agents
share the same strictly-positive prior and have a common public
self-evident event $F$ on which each agent's posterior of an event
$E$ is constant, the two constants must be equal. The proof rests
on a cell-decomposition lemma (\TT{selfEvident\_sum\_decomp}):\
a self-evident event is the disjoint union of its contained
$P$-cells, so any $\mu$-sum over $F$ decomposes into per-cell
sums. Since the posterior is constant per cell (by the partition
structure) and constant on $F$ (by hypothesis), every cell-sum is
the same multiple of its $\mu$-mass, and the two agents both
recover the marginal $\mu(E \mid F)$. This is the operationally
useful form of ``agents with common knowledge of posteriors must
agree'':\ in any common-knowledge situation about posteriors the
posteriors are constant on the public event, and the result
applies.

\paragraph{Approximate common belief.}\
The approximate layer \TT{ApproximateCommonKnowledge.lean} adds
common $p$-belief in the Monderer--Samet style.  The event
\TT{PBelief} records states where an agent assigns posterior at
least $p$ to an event, \TT{IsPEvident} says that a support event is
$p$-believed whenever true, and \TT{CommonPBeliefAt} packages the
usual finite witness: a $p$-evident event containing the state and
contained in mutual $p$-belief of the target event.  Exact common
knowledge implies common $p$-belief for every $p \le 1$ under a
strictly positive prior.  The file also ports the quantitative
agreement bound formalized by
\citet{ChenEtAl2026AgreeDisagreeFormal}: if it is common $p$-belief
that each player $i$ reports posterior $r_i$ for event $E$, then
any two reports satisfy
\[
  |r_i - r_j| \le 2(1-p).
\]
The Lean theorem is
\TT{commonPBelief\_posterior\_reports\_close}.

\leancorr{\TT{Concepts/Knowledge/CommonKnowledge.lean} (\TT{InfoPartition},
\TT{Knows}, \TT{Knows\_subset} (T), \TT{Knows\_idem} (4),
\TT{Knows\_not\_Knows} (5), \TT{Knows\_mono}, \TT{Knows\_inter},
\TT{isSelfEvident\_iff\_Knows\_eq}, \TT{posterior},
\TT{agree\_to\_disagree}, \TT{mutualKnowledge},
\TT{CommonKnowledgeAt}, \TT{CommonKnowledgeAt.idem},
\TT{cells\_disjoint}, \TT{selfEvident\_eq\_biUnion\_cells},
\TT{selfEvident\_sum\_decomp}, \TT{aumann\_full\_agreement});
\TT{Concepts/Knowledge/ApproximateCommonKnowledge.lean} (\TT{PBelief},
\TT{mutualPBelief}, \TT{IsPEvident}, \TT{CommonPBeliefAt},
\TT{CommonKnowledgeAt.commonPBeliefAt},
\TT{commonPBelief\_posterior\_reports\_close}).}

\subsection{Individual rationality}
\label{sec:solution-concepts:ir}

A profile is \emph{individually rational} for player $i$ when $i$'s
payoff is at least their security level
(\Cref{sec:solution-concepts:security}).  This participation
constraint is formal scaffolding for the mechanism-design layer
(\Cref{sec:mechanism-auctions}).  The repeated-game folk theorem uses
the related opponent-enforced mixed minmax vector
$m_i(\KG^{\mathrm{mix}})$, defined in \Cref{sec:theorems:folk}, as
its strict individual-rationality threshold.

\leancorr{\TT{Concepts/Welfare/IndividualRationality.lean}.}

\subsection{Babbling and cheap talk}
\label{sec:solution-concepts:babbling}

The library also records the standard babbling-equilibrium argument
for observable cheap talk.  A cheap-talk extension of a game form
adds, for each player, a message and a contingent action plan from
the realized message profile to a base-game strategy.  The canonical
\emph{babbling} embedding sends a fixed default message and ignores
all messages when choosing the base action.

The packaged theorem is deliberately one-way: every base Nash
equilibrium embeds as a babbling Nash equilibrium of the cheap-talk
extension.  It does not say that cheap talk preserves all equilibria:
observable messages may introduce additional coordination equilibria.
The proof assumes only the local condition needed for babbling, namely
that around an embedded base profile every unilateral enriched
deviation projects to a base unilateral deviation with the same
preference comparison.  Concretely, if a deviator changes both their
message and their message-contingent plan, the local condition extracts
the base action that would actually be played after the fixed babbling
message profile and compares that base deviation instead.

\leancorr{\TT{Core/Babbling.lean} defines the protocol-level
\TT{CheapTalkExtension} and local preservation condition;
\TT{Concepts/Communication/Babbling.lean} proves the \TT{GameForm} and
\TT{KernelGame} Nash corollaries; \TT{Languages/NFG/CheapTalkExamples.lean}
instantiates the result for Battle of the Sexes.}
