\section{A worked example end-to-end: Prisoner's Dilemma}
\label{sec:worked-example}

To anchor the abstractions of \S\ref{sec:semantic-core}--%
\S\ref{sec:languages}, we trace one small game through the full
syntax-to-theorem pipeline.  The example is deliberately the
smallest non-trivial one — Prisoner's Dilemma in NFG form — and
the corresponding Lean is in
\TT{Languages/NFG/Examples.lean}.

\paragraph{Source syntax.}\
The player type is $\Players = \mathrm{Bool}$, the action type is
\[
  \Act \;=\; \{\textsf{cooperate},\,\textsf{defect}\},
\]
shared between both players, and the payoff matrix is the
classical one ($r_{CC} = 2$, $r_{DD} = 1$, $r_{DC} = 3$ for the
defector and $0$ for the cooperator).  As an \TT{NFGGame}, this is
a record carrying the joint outcome type
$\prod_{i:\mathrm{Bool}} \Act$, the identity outcome map, and the
$\mathrm{Bool} \times \Act \times \Act \to \RR$ utility table.

\paragraph{Compilation to a kernel game.}\
The NFG compiler (\S\ref{sec:languages:nfg}) sets the strategy type
to $\Act$ for each player, the outcome type to
$\prod_i \Act$, the kernel to the Dirac evaluation
$\Profile \mapsto \Dirac_\Profile$, and the utility to the input
table.  The resulting \TT{KernelGame} is deterministic; randomness
enters only when we lift to its mixed extension
(\S\ref{sec:semantic-core:kernelgame}).

\paragraph{Solution-concept instantiation.}\
The library's $\IsNash$ predicate
(\S\ref{sec:solution-concepts:nash}) on the compiled kernel game
unfolds to
\[
  \forall i \in \{T, F\},\,\forall a' \in \Act.\quad
    u_i(\Profile) \;\ge\; u_i(\Profile[i \mapsto a']),
\]
which on Prisoner's Dilemma reduces to four inequality checks per
profile.  The Lean proof
$\TT{pd\_defect\_is\_nash}$:\
\TT{IsNashPure prisonersDilemma pd\_defect\_defect} is a single
\TT{intro/cases/cases/simp} that discharges the four inequalities
by direct evaluation of the utility table.  The corresponding
``cooperate is not Nash'' fact is the symmetric \TT{linarith} after
unfolding the deviation to defect.

\paragraph{Mixed-strategy extension and Nash existence.}\
Lifting to the mixed extension produces a kernel game with
strategy type $\PMF{\Act}$ for each player and outcome type
$\prod_i \Act$ as before.  The library's mixed Nash existence
theorem (\Cref{thm:nash-mixed}) applies nonconstructively and
returns some mixed equilibrium of the extension.  Separately, the
worked example proves that defect is dominant, so the pure
(defect, defect) profile is Nash by the
dominance$\,\Rightarrow\,$Nash chain
(\S\ref{sec:solution-concepts:dominance}) without invoking Brouwer.

\paragraph{Bridging to FOSG.}\
The NFG$\to$FOSG bridge of \S\ref{sec:languages:bridges} maps
Prisoner's Dilemma to a one-shot FOSG with two world states
($\mathsf{init}, \mathsf{terminal}$), every player active at
$\mathsf{init}$, no observations, and a single deterministic
transition delivering the NFG payoff as the FOSG reward.  The
bridge theorem
\TT{NFG\_FOSG.NFGGame.toFOSG\_terminal\_iff} closes the
expressiveness contract:\ the EU of any pure profile in the FOSG
agrees with the EU in the NFG, so $\Profile^*$ remains a Nash
equilibrium under the EU-isomorphism transport
(\Cref{thm:transport}).

\paragraph{What this trace illustrates.}\
\emph{(i)} The NFG syntax is a $\sim$30-line Lean record;
\emph{(ii)} compilation to \TT{KernelGame} is a definitional
unfolding, not a proof;
\emph{(iii)} the strategic-form theorems
(dominance$\Rightarrow$Nash; mixed existence; equilibrium
preservation under bridges) apply as black boxes once the
compilation has fixed the kernel game;
\emph{(iv)} the same game appears as a different syntactic
object in two languages (NFG and FOSG) but with definitionally
equal expected utility, so any equilibrium-level theorem proved
on one of them transports to the other.

The same trace works for any NFG of finite cardinality.  The
\TT{Examples.lean} file in \TT{Languages/NFG/} carries the
analogous one-paragraph treatments for Matching Pennies (no pure
equilibrium), Stag Hunt and Battle of the Sexes (two pure
coordination equilibria), Hawk–Dove (two anti-coordination
equilibria), Dictator and Traveler's Dilemma (asymmetric
contents), and Cournot duopoly (a richer payoff matrix with
discrete quantities and a $\textsf{q}_2{=}\textsf{q}_2$ Nash).
A parallel trace for an EFG (e.g.\ a two-step centipede) is
recorded in \TT{Languages/EFG/Examples.lean}; we omit the latter
here for space.
