\section{Major theorems}
\label{sec:theorems}

The library proves the central existence and structural theorems
of finite non-cooperative game theory.  The proofs are stated on
the kernel-game/game-form layer (or on layered information-model
abstractions; see \Cref{sec:theorems:kuhn}), and inherited by
every language via $\compileTo$.  This section sketches their
content; full proofs are in the cited Lean files.

\subsection{Existence of mixed Nash equilibria}
\label{sec:theorems:nash-mixed}

\begin{theorem}[Mixed Nash existence; \TT{KernelGame.mixed\_nash\_exists\_of\_bounded}]
\label{thm:nash-mixed}
Let $\KG$ be a kernel game with $\Players$ finite, every $\Strat_i$
finite and non-empty, and player utilities bounded on outcomes:
there are constants $C_i$ such that
$|\util(\omega,i)| \le C_i$ for all $\omega$ and $i$.  No finiteness
assumption is needed on $\Outcome$.  Then the mixed extension
$\KG^{\mathrm{mix}}$ admits a Nash equilibrium:\ a
profile $\Profile^* \in \prod_i \PMF{\Strat_i}$ with
\[
  \forall i,\,\forall \tau \in \PMF{\Strat_i}.\quad
    \EU(\KG^{\mathrm{mix}}, \Profile^*, i)
      \;\ge\;
    \EU(\KG^{\mathrm{mix}}, \Profile^*[i \mapsto \tau], i).
\]
\end{theorem}

\noindent\emph{Proof structure.}\ Following Nash's
original~\citep{Nash1950, Nash1951}, we define the gain map
\[
  \Phi_i(\Profile)(s)
    \;=\; \frac{\Profile_i(s) + (\mathrm{gain}_i(\Profile, s))^+}
              {1 + \sum_{s'} (\mathrm{gain}_i(\Profile, s'))^+},
  \qquad
  \mathrm{gain}_i(\Profile, s)
    \;=\;
    \EU(\KG^{\mathrm{mix}}, \Profile[i \mapsto \Dirac_s], i)
      - \EU(\KG^{\mathrm{mix}}, \Profile, i),
\]
which sends the product simplex $\prod_i \Delta(\Strat_i)$
continuously into itself.  The Brouwer fixed-point theorem from
the \TT{fixed-point-theorems-lean4}
package~\citep{harfeFixedPointTheorems} is lifted to the product
of standard simplices, and a fixed point of $\Phi$ is shown to be
a Nash equilibrium by an algebraic argument bracketing the positive
parts.  The bounded-utility hypothesis supplies the convergence
facts for expected utility; the finite-outcome theorem
\TT{KernelGame.mixed\_nash\_exists} is the wrapper that obtains
such a bound automatically.

\paragraph{Why a topological route.}  The continuity content of the
proof — that the Nash map is continuous on a compact convex
polytope — is genuinely topological, and mechanizing the topology
of the simplex from scratch would dwarf the rest of the proof.  The
\TT{fixed-point-theorems-lean4} package supplies the Brouwer theorem;
mathlib supplies the surrounding finite-dimensional topology,
compactness/convexity infrastructure, and continuity API needed to
instantiate it on the product of simplices.  The product-of-simplices
step is handled by an explicit product-fixed-point lemma rather than
by appealing to the product theorem in topology.

\tradeoff{The imported Brouwer theorem is exposed through classical
topology, so mixed Nash existence is \TT{noncomputable}.  Although the
standalone \TT{fixed-point-theorems-lean4}
package~\citep{harfeFixedPointTheorems} proves Brouwer via a cubical
Sperner's-lemma route~\citep{Kuhn1960}, the surrounding compactness,
continuity, and fixed-point API does not extract an algorithmic
witness.  A constructive existence theorem in the computational sense
would require either an explicit equilibrium algorithm
(Lemke–Howson~\citep{LemkeHowson1964} for two-player games, or
support enumeration for finite games more generally) or a separate
constructive fixed-point development tailored to finite strategy
simplices.  Algorithm-level Nash existence is independent enough to
live in a downstream module.}

\leancorr{Statements \TT{KernelGame.mixed\_nash\_exists\_of\_bounded}
and \TT{KernelGame.mixed\_nash\_exists} in
\TT{Theorems/NashExistenceMixed.lean}; the product-simplex
Brouwer wrapper in \TT{Concepts/ProductSimplexBrouwer.lean}.
Supplement~§6.1.}

\subsection{Existence of correlated and coarse correlated equilibria}
\label{sec:theorems:correlated-existence}

\begin{theorem}[CE / CCE existence; \TT{KernelGame.correlatedEq\_exists\_of\_bounded}, \TT{coarseCorrelatedEq\_exists\_of\_bounded}]
\label{thm:ce-exists}
Under the same finite-player, finite-strategy, non-empty-strategy,
and bounded-utility hypotheses as
\Cref{thm:nash-mixed}, $\KG$ admits a correlated equilibrium and a
coarse correlated equilibrium.
\end{theorem}

\noindent\emph{Proof.}\ The independent product distribution
$\bigotimes_i \Profile^*_i$ over the mixed Nash profile
$\Profile^*$ of \Cref{thm:nash-mixed} is a correlated equilibrium
of the original $\KG$ (every recommendation-dependent deviation
factors through a constant-strategy unilateral deviation in
$\KG^{\mathrm{mix}}$).  The reason is that, after a recommendation
$s_i$ is drawn from the product distribution, replacing it by
$d_i(s_i)$ is exactly the mixed-game unilateral deviation that samples
$s_i$ and then plays $d_i(s_i)$.  CCE existence is the corollary
$\Pref\text{-CE}\subseteq\Pref\text{-CCE}$
(\Cref{sec:solution-concepts:correlated}).

\tradeoff{This route gives CE existence as a corollary of
mixed Nash existence and is the cleanest path through the
finite-strategy machinery used by the proof.  Hart and
Mas-Colell's regret-matching no-regret learning
construction~\citep{HartMasColell2000} produces CCE existence
constructively without going through Brouwer.  We have not
formalized regret-matching itself, but the existence theorem is
still available as a corollary of Nash existence; if a future
constructive Nash-existence proof becomes available the dependency
inverts trivially.}

\leancorr{\TT{KernelGame.correlatedEq\_exists\_of\_bounded},
\TT{KernelGame.correlatedEq\_exists},
\TT{KernelGame.coarseCorrelatedEq\_exists\_of\_bounded}, and
\TT{KernelGame.coarseCorrelatedEq\_exists} in
\TT{Theorems/CorrelatedEqExistence.lean}.  Supplement~§6.2.}

\subsection{The minimax theorem}
\label{sec:theorems:minimax}

\begin{theorem}[Von Neumann's minimax; \TT{KernelGame.von\_neumann\_minimax\_of\_bounded}]
\label{thm:minimax}
Let $\KG$ be a two-player zero-sum kernel game with finite
non-empty strategy spaces and bounded utilities, and write the two
players as $0$ and $1$.  There exist a real value $v$ and a mixed
Nash profile $\sigma$ of
$\KG^{\mathrm{mix}}$ such that player $1$ cannot push player $0$'s
payoff below $v$ by deviating from $\sigma_1$, and player $0$ cannot
push their payoff above $v$ by deviating from $\sigma_0$:
\[
  \EU(\KG^{\mathrm{mix}}, \sigma, 0) = v,\qquad
  \forall s_1,\ \EU(\KG^{\mathrm{mix}}, \sigma[1 \mapsto s_1], 0) \ge v,
\]
\[
  \forall s_0,\ \EU(\KG^{\mathrm{mix}}, \sigma[0 \mapsto s_0], 0) \le v.
\]
Moreover, all mixed Nash equilibria of a two-player zero-sum game
give player $0$ the same expected utility.
\end{theorem}

\noindent\emph{Proof.}\ \Cref{thm:nash-mixed} gives existence of a
mixed Nash equilibrium.  In a two-player zero-sum game, mixed Nash
profiles give saddle-style inequalities for $\EU(\cdot, 0)$,
which combine with the zero-sum-Nash equality lemma and mixed Nash
existence to deliver the displayed guarantees.  The classical
max-min/min-max equality is the standard mathematical reading of
the finite saddle inequalities; the Lean theorem is stated in the
guarantee form above.

\leancorr{Statements \TT{KernelGame.von\_neumann\_minimax} and
\TT{KernelGame.von\_neumann\_minimax\_of\_bounded} in
\TT{Theorems/Minimax.lean}; supporting zero-sum-Nash equality in
\TT{Concepts/ZeroSumNash.lean} (\TT{IsZeroSum.nash\_eu\_eq}).
Supplement~§6.3.}

\subsection{Discounted folk theorem approximation}
\label{sec:theorems:folk}

The library includes an infinite discounted repeated-game theorem
separate from the bounded multi-round syntax of
\Cref{sec:languages:multiround}.  It uses a public profile-history
semantics:\ a period observation is the realized \TT{KernelGame}
profile.  In the main theorem below the repeated game is formed over
the mixed extension, so those public observations are mixed-action
profiles.  For a kernel game $\KG$, write
$F(\KG)$ for the convex hull of pure-profile payoff vectors and
write $m_i(\KG^{\mathrm{mix}})$ for the opponent-enforced mixed
minmax value:
\[
  m_i(\KG^{\mathrm{mix}})
    \;=\;
  \inf_{\tau_{-i}}\; \sup_{\tau_i}\,
    \EU(\KG^{\mathrm{mix}},(\tau_i,\tau_{-i}),i).
\]
The strict individually rational feasible region is
\[
  \{v \in F(\KG) : \forall i,\; m_i(\KG^{\mathrm{mix}}) < v_i\}.
\]

\begin{theorem}[Approximate discounted folk theorem for observable mixed actions]
\label{thm:folk-discounted}
Let $\KG$ have finitely many players, finite non-empty pure
strategy spaces, and finite outcomes.  If
\[
  v \in F(\KG)
  \quad\text{and}\quad
  \forall i,\; m_i(\KG^{\mathrm{mix}}) < v_i,
\]
then $v$ is approachable by Nash equilibrium payoffs of the
observable mixed-action discounted repeated game over
$\KG^{\mathrm{mix}}$:\ for every
$\epsilon>0$ there is $\delta_0<1$ such that every
$\delta\in(\delta_0,1)$ admits a discounted repeated-game Nash
equilibrium $\Sigma^\delta$ with payoff $w^\delta$ satisfying
\[
  \forall i,\qquad |w^\delta_i - v_i| < \epsilon .
\]
\end{theorem}

\noindent\emph{Proof structure.}\ The proof follows the classical
Friedman/Fudenberg--Maskin trigger-strategy pattern
\citep{Friedman1971,FudenbergMaskin1986}, with all approximation
constants made explicit.
\begin{itemize}\itemsep2pt
\item A feasible payoff $v$ is represented as a finite convex
combination of pure-profile payoffs.  The denominator-clearing
lemma in \TT{Math/SimplexApproximation.lean} floors all weights
except one residual coordinate and proves a uniform error bound.
This yields a finite pure-profile cycle whose uniform average
payoff is within a chosen tolerance of $v$.

\item Strict individual rationality supplies a positive uniform
margin $\eta$ above the opponent-enforced mixed minmax vector.
For each player the proof chooses an approximate punishment
opponent profile whose best response value is below
$m_i(\KG^{\mathrm{mix}})+\eta/4$.

\item The repeated-game strategy follows the finite cycle until a
public deviation is detected; after that, every non-deviating
player switches permanently to the deviator's punishment profile.
The formal definition uses public histories and a recursive
\TT{triggerStatus} detector, rather than finite-horizon
multi-round syntax.

\item Two discount-factor thresholds are combined: one makes every
discounted continuation payoff of every phase of the periodic
cycle close to the cycle average, and one ensures that the
one-period deviation gain is dominated by the discounted
continuation loss from punishment.  The trigger profile is then
proved Nash for all $\delta$ above the common threshold, and its
payoff is within $\epsilon$ of $v$.
\end{itemize}

\tradeoff{The theorem is stated for the repeated game over the
mixed extension, so a period action is an observable mixed stage
strategy, not a sampled pure action generated by hidden private
randomization.  This is a precise public mixed-action folk theorem
and avoids adding sampled action histories or correlated public
randomization to the language layer.  A richer behavioral
repeated-game semantics could refine the interface later; the
payoff-set approximation and trigger-incentive proof already
isolate the main analytic work.}

\leancorr{\TT{Concepts/FolkTheorem.lean} defines feasible payoff
sets, opponent minmax values, discounted repeated strategies,
periodic paths, trigger strategies, and
\TT{discounted\_folk\_theorem\_approx}.  The generic
denominator-clearing estimate is in
\TT{Math/SimplexApproximation.lean}.}

\subsection{Backward induction (Zermelo) and the one-shot deviation principle}
\label{sec:theorems:zermelo-odp}

A \emph{subgame-perfect equilibrium}~\citep{Selten1965} (SPE) of
an extensive-form game is a strategy profile that is a Nash
equilibrium not just of the whole game but of every subgame:\ the
restriction of $\sigma$ to any decision node and its descendants
is itself Nash on the subtree rooted there.  This rules out
``empty threats''  — Nash profiles that prescribe a player to do
something off-path that they would not actually want to do if the
off-path subgame were reached.  In a finite perfect-information
tree, SPE is the standard refinement of Nash equilibrium, and is
the equilibrium concept the theorems below characterize.

\begin{theorem}[One-shot deviation principle]
\label{thm:odp}
Let $G$ be a finite perfect-information extensive-form game.  A pure
profile $\sigma$ is a subgame-perfect equilibrium of $G$ iff it has
no profitable one-shot deviation:\ at every reachable decision node,
the action prescribed by $\sigma$ yields at least as much expected
utility (holding the rest of $\sigma$ fixed) as any alternative.
In Lean the main statement is the bounded-utility theorem; the
finite-outcome statement is a wrapper that derives boundedness.
\end{theorem}

\begin{theorem}[Zermelo's backward induction]
\label{thm:zermelo}
Every finite perfect-information extensive-form game has a pure
subgame-perfect equilibrium.
The formal theorem again has a bounded-utility form without a finite
outcome carrier, plus a finite-outcome wrapper.
\end{theorem}

\noindent The backward induction itself constructs, by recursion
on the tree, a profile with no profitable one-shot deviation; the
ODP closes the loop to subgame-perfection.  Two non-trivial
ingredients are worth flagging:
\begin{itemize}\itemsep2pt
\item \emph{Disjointness of subtrees in perfect-info trees}:\ in
a perfect-info tree, sibling subtrees have disjoint information-set
supports.  This is what allows backward induction to fix actions
at a decision node without breaking optimality elsewhere.

\item \emph{Reachable-decision quantification}:\ the ODP's
hypothesis quantifies over reachable decision nodes only.  An
explicit reach-by relation makes this precise and lets the proof
ignore unreachable nodes whose action choice cannot affect EU.
\end{itemize}

\tradeoff{Backward induction is constructively well-defined on a
finite tree, but the library's Zermelo is \TT{noncomputable}
because intermediate steps invoke classical reasoning to compare
real-valued utilities.  A computable variant restricting to
rational utilities would compile but is not packaged.}

\leancorr{Statements \TT{EFG.oneShotDeviation\_iff\_spe\_of\_bounded},
\TT{EFG.oneShotDeviation\_iff\_spe}, \TT{EFG.zermelo\_of\_bounded},
and \TT{EFG.zermelo} in \TT{Theorems/OneShotDeviation.lean} and
\TT{Theorems/Zermelo.lean}; the subtree disjointness lemma is
\TT{perfectInfo\_disjoint\_subtrees}; the reachability relation
is \TT{EFG.ReachBy}.  Supplement~§6.4.}

\subsection{Kuhn's theorem: \texorpdfstring{behavioral $\leftrightarrow$ mixed strategies}{behavioral vs. mixed strategies}}
\label{sec:theorems:kuhn}

Kuhn's theorem~\citep{Kuhn1953} relates two carriers of randomness
in extensive-form games:\ a \emph{mixed strategy} is a
distribution over pure strategies (a single global lottery),
while a \emph{behavioral strategy} chooses an independent local
lottery at each information set.  The two are payoff-equivalent
under recall conditions; without recall, the asymmetry is
genuine.

The library proves Kuhn's theorem on a representation-neutral
substrate, the \emph{observation model}:\ a tuple
$(W, \mathrm{Obs}, \Act)$ recording the world-state type, each
player's observation type, and the per-observation action arity.
A behavioral profile is a per-player function
$\InfoState_i \to \PMF{\Act_i}$; a mixed profile is a per-player
distribution over the deterministic functions
$\InfoState_i \to \Act_i$.\footnote{Notational reconciliation:\
the Lean code uses \TT{runDist}/\TT{runDistPure} for the
profile-evaluation function on the observation-model carrier; we
write $\evalDist$ throughout the chapter for uniformity with the
EFG-language naming.  The two refer to the same operation
specialized to the relevant carrier.}

\begin{theorem}[Kuhn behavioral $\to$ mixed]
\label{thm:kuhn-bm}
Under the bounded-horizon hypothesis (no infinite traces) and the
\emph{no-non-trivial info-state repeat} hypothesis, every
behavioral profile $\beta$ admits an equivalent mixed profile
$\mu(\beta)$ in the sense
\[
  \evalDist(\beta) \;=\; \mu(\beta) \mathbin{\bind} \evalPure.
\]
\end{theorem}

\begin{theorem}[Kuhn mixed $\to$ behavioral]
\label{thm:kuhn-mb}
Under per-step semantic locality assumptions (sufficient for the
\emph{ActionPosteriorLocal} property), every mixed profile $\mu$
admits an equivalent behavioral profile $\beta(\mu)$ in the sense
\[
  \evalDist(\beta(\mu)) \;=\; \mu \mathbin{\bind} \evalPure.
\]
\end{theorem}

\noindent The two directions are not symmetric.  $B \to M$ does
not need recall — the mixed lottery can be constructed
ex-ante by independent product across information states — but
does need horizon-separation (which holds on snapshot-refined
$\InfoState$'s).  $M \to B$ requires the per-step recall property
that, given a player's information state, the conditional
distribution of their action under $\mu$ does not depend on
information \emph{outside} the player's recall.  This is
strictly weaker than perfect recall in the textbook sense:\ it
does not require remembering one's own past observations
literally, only that the action conditional has the right
locality.

The snapshot-refined information-state structure is packaged as a
derived layer on top of an arbitrary observation model.  A second
proof of the $M \to B$ direction avoids the snapshot-refined
infrastructure by deriving the behavioral strategy from the correlated
distribution induced by a mixed Nash profile.  Language-specific Kuhn
theorems for EFG, MAID, MR, and FOSG follow by composing the language's
compilation to the observation-model layer with the generic theorem.

\tradeoff{Stating Kuhn on the observation-model layer rather than
on a specific syntactic class of EFGs is the single largest piece
of abstraction work in the library.  The benefit is that one proof
serves every language with a generic compilation through that
layer; the cost is a stack of technical infrastructure
(information-state snapshots, the locality predicates) that is not
in the textbook proof.  We judge the tradeoff to be sharply
positive:\ language-specific Kuhn theorems become single-line
corollaries of a single core result.}

\leancorr{\TT{Theorems/Kuhn/} contains \TT{ObsModel} (the
snapshot-refined wrapper), \TT{ObsModelCore}, \TT{KuhnModel}, the
two proof files \TT{BehavioralToMixedCore} and
\TT{MixedToBehavioralCore}, and \TT{CorrelatedRealization} (the
alternative $M \to B$ route).  The hypothesis predicates
\TT{NoNontrivialInfoStateRepeat}, \TT{HorizonSeparation},
\TT{ActionPosteriorLocal}, \TT{PerStepPlayerRecall} live on
\TT{ObsModelCore}.  Supplement~§6.5.}

\subsection{Welfare and welfare theorems}
\label{sec:theorems:welfare}

The definitions and basic welfare/Pareto bridge are in
\Cref{sec:solution-concepts:welfare}.  This theorem layer packages
the finite existence wrappers
(\TT{exists\_welfareMax}, \TT{exists\_paretoEfficient}) and the
team-game corollaries used by the price-of-stability result.  We do
not formalize the deeper welfare theorems of mechanism design here
— they live in \Cref{sec:mechanism-auctions}.

\leancorr{\TT{Concepts/WelfareTheorems.lean};
\TT{Concepts/NashPareto.lean}.}

\subsection{Shapley value uniqueness}
\label{sec:theorems:shapley-uniqueness}

This theorem belongs to the cooperative branch
(\TT{Cooperative/CoalitionalGame.lean}) — formally a parallel
paradigm to the non-cooperative core that occupies the rest of
the library (see \Cref{sec:future:cooperative} for the framing).
We state it here because it has the standing of a flagship
finite-game-theory theorem and because the proof technique it
uses (unanimity-basis decomposition, an instance of Möbius
inversion on the subset lattice) is the same Mathlib-style finite
combinatorics that powers \Cref{sec:theorems:nash-mixed}
on the non-cooperative side.

A TU coalitional game on a finite player set $\Players$ is a
characteristic function $v : 2^{\Players} \to \RR$ with
$v(\emptyset) = 0$.  An \emph{allocation} is a function
$\phi : \mathrm{CoalGame} \to \Players \to \RR$.

\begin{theorem}[Shapley uniqueness, after \citealp{Shapley1953}]
\label{thm:shapley-unique}
Let $\phi$ be any allocation rule satisfying:
\emph{(efficiency)} $\sum_i \phi(G)_i = G.v(\Players)$;
\emph{(symmetry)} symmetric players receive equal value;
\emph{(null player)} a player whose marginal contribution is
identically zero receives $0$;
\emph{(additivity)} $\phi(G_1 + G_2) = \phi(G_1) + \phi(G_2)$;
and \emph{(scalar homogeneity)} $\phi(c \cdot G)_i = c \cdot
\phi(G)_i$.
Then $\phi$ coincides with the Shapley value on every $G$.
\end{theorem}

The proof first establishes \emph{value on unanimity games}:\ the
three axioms (efficiency, symmetry, null) determine $\phi$ on the
indicator games $u_S$ (where $u_S(T) = 1$ iff $S \subseteq T$).
Then the unanimity-basis decomposition expresses every $G$ as
$\sum_{S \subseteq \Players} c_S \cdot u_S$ (sum of TU games) with Möbius
coefficients $c_S = \sum_{R \subseteq S} (-1)^{|S \setminus R|}
G.v(R)$.  Linearity of $\phi$ (additivity + scalar) then propagates
the value from unanimity games to all of $G$.

\paragraph{Modern axiom set.}\
The classical theorem uses additivity alone and recovers scalar
homogeneity for rationals via the $n \cdot \phi(G) = \phi(n \cdot
G)$ argument.  Extending from $\mathbb{Q}$ to $\mathbb{R}$ requires
either a continuity hypothesis or full scalar homogeneity as a
primitive axiom.  The library adopts the modern formulation with
linearity (= additivity + scalar) as a primitive — this is the
formulation in most current textbook treatments and lets the proof
stay purely combinatorial.

\leancorr{\TT{Cooperative/CoalitionalGame.lean}
(\TT{shapleyValue}, \TT{shapleyValue\_unique}); supporting
infrastructure \TT{unanimityGame}, \TT{unanimityCoeff},
\TT{unanimity\_decomposition}, \TT{allocation\_on\_unanimityGame},
\TT{gameSum}, \TT{gameSum\_allocation\_eq},
\TT{eq\_gameSum\_decompTerm}.}

\paragraph{Core certificates from the unanimity basis.}\
The same decomposition also supports core-membership proofs.  The
library proves that the core is closed under sums of games and
under nonnegative scalar multiplication of both games and
allocations.  Since the Shapley value of a unanimity game lies in
that unanimity game's core, any game whose unanimity-basis
coefficients are all nonnegative has its Shapley value in the
core.  This is the positive-cone statement exposed by
\TT{shapleyValue\_isCore\_of\_nonneg\_unanimityCoeff}; it is
deliberately stated at the coefficient level, so later convex-game
arguments can reuse the closure layer without duplicating the
Möbius-decomposition proof.

\subsection{Gale–Shapley stable-matching existence}
\label{sec:theorems:gale-shapley}

Like \Cref{sec:theorems:shapley-uniqueness}, this result belongs to
the cooperative branch (\TT{Cooperative/GaleShapley.lean}); we state
it among the major theorems because stable-matching existence is a
flagship constructive result of finite game theory.  A
\emph{two-sided matching market} on finite sides $\alpha$ and $\beta$
gives each agent a strict (injective) ranking of the opposite side; a
matching is \emph{stable} when no \emph{blocking pair} exists — two
agents who each prefer the other to their assigned partner.

\begin{theorem}[Gale–Shapley existence, after \citealp{GaleShapley1962}]
\label{thm:gale-shapley}
Every finite matching market with strict preferences admits a stable
matching.
\end{theorem}

\noindent\emph{Proof structure.}\ Deferred acceptance is formalized
not as well-founded recursion but as an \emph{inflationary rejection
operator} on the proposal state
$R : \alpha \to \mathrm{Finset}\,\beta$ recording, for each proposer,
the recipients that have already rejected it.  One round \TT{daStep}
has every not-currently-held proposer approach its favourite remaining
recipient, and every recipient tentatively hold its best suitor while
rejecting the rest; the rejection sets only grow.  Because the total
rejection count is bounded by $|\alpha|\cdot|\beta|$ and is monotone,
a pigeonhole argument produces a \emph{fixed point} $R^\star$ — a
round that rejects nobody.  The matching read off from $R^\star$'s
holders is shown to be a matching, individually rational, and free of
blocking pairs via the \emph{deferred-acceptance invariant}:\
whenever a recipient has rejected a proposer, it currently holds
someone it strictly prefers.  Strictness of preferences is
load-bearing exactly in maintaining that invariant; the
no-blocking-pair conclusion then needs no further hypothesis.

\tradeoff{The construction is fully constructive on the finite market,
but the library's \TT{exists\_stable} is \TT{noncomputable} because
the argmax over remaining choices and the fixed-point extraction route
through classical choice.  Extracting the $O(n^2)$ algorithm as a
computable function with the same correctness proof is a natural
refinement.  The theorem fixes the proposing side; the companion
optimality results (the proposing side receives its best stable
partner, the lattice structure of stable matchings) are not yet
formalized.}

\leancorr{\TT{Cooperative/GaleShapley.lean}
(\TT{MatchingMarket}, \TT{daStep},
\TT{exists\_daStep\_iterate\_fixed}, \TT{fixedPoint\_isMatching},
\TT{fixedPoint\_ir}, \TT{exists\_stable}); the stability predicates
\TT{IsMatching}/\TT{IsBlockingPair}/\TT{IsStable} are reused from
\TT{Cooperative/Matching.lean}.}
