\section{Future directions}
\label{sec:future}

The library is intentionally a foundation:\ it is meant to be
extended.  We list the extensions we view as natural, in
descending order of how much existing infrastructure they would
re-use.

\subsection{Algorithmic and constructive Nash}
\label{sec:future:algo}

\Cref{thm:nash-mixed} is non-constructive (Brouwer); a natural
extension is a constructive proof for two-player games via the
\emph{Lemke–Howson} pivoting algorithm~\citep{LemkeHowson1964} or
via \emph{Sperner's lemma}~\citep{Sperner1928} (a combinatorial
fixed-point statement on triangulated simplices that yields
Brouwer constructively for low dimensions), packaged as an
algorithmic witness function on top of the existing strategic-form
definitions.  The \emph{PPAD}-hardness
story~\citep{DaskalakisGoldbergPapadimitriou2009} — where PPAD is
the complexity class of problems whose existence is guaranteed by
a parity argument on a directed graph, the canonical example being
end-of-line — is at a different level (it concerns problem
reductions, not proof-of-existence) and is largely orthogonal:\ a
complexity formalization would need an independent computation
model.

\subsection{Sequence form and efficient EFG solving}
\label{sec:future:sequence-form}

A \emph{sequence} in an extensive-form game with perfect recall is
the list of own-actions a player has taken along a history.  The
\emph{sequence-form representation}
of~\citet{KollerMegiddoVonStengel1994} (see also the survey
of~\citet{vonStengel2002}) replaces the exponential-sized pure
strategy space by realization probabilities indexed by sequences,
turning equilibrium computation into a linear or quadratic
program of size polynomial in the tree.  Adding the sequence-form bridge as a fourth EFG
strategy carrier (alongside pure, behavioral, mixed) would let
the library state and prove correctness of the standard solving
algorithms (LP duality$\Rightarrow$two-player zero-sum value;
sequence-form quadratic program for general-sum games).  The
Kuhn-theorem infrastructure of \S\ref{sec:theorems:kuhn} already
supplies the recall layer.

\subsection{Counterfactual regret minimization}
\label{sec:future:cfr}

\emph{Counterfactual regret minimization} (CFR,
\citealp{Zinkevich2007CFR}) is the dominant family of algorithms
for finding approximate equilibria in large imperfect-information
extensive-form games; it works by tracking, at each information
set, the cumulative regret for not having played each action,
counterfactually weighted by the probability of reaching that
information set under the opponents' play.  The regret-equilibrium
duality is already formalized in the library
(\S\ref{sec:solution-concepts:regret}), making the CFR convergence
proof a natural consumer.  This would also produce a
constructive CCE existence theorem
(\S\ref{sec:theorems:correlated-existence}) without going through
Brouwer.

\subsection{Imperfect-recall extensions}
\label{sec:future:absent-mind}

The Kuhn theorem in the library handles a recall hypothesis
weaker than perfect recall (per-step ActionPosteriorLocal).  A
natural extension is to formalize the
\emph{absent-minded-driver} phenomenon~\citep{PiccionePiccione1997}
— a single-player imperfect-recall puzzle where a player who
forgets whether they have already made one decision faces a
time-consistency problem (the ex-ante optimal mixed strategy is
not the same as the strategy the player would choose at the
decision point if they could) — and the broader family of
imperfect-recall pathologies it generates.  These require exactly
the representation-neutral observation model the library already
exposes.

\subsection{Infinite and continuous games}
\label{sec:future:infinite}

The largest single extension would be to relax the discrete-PMF
discipline and use mathlib's measure theory.  This would let the
library state and prove:\ Glicksberg's theorem on continuous
payoff functions over compact strategy
spaces~\citep{Glicksberg1952}, the Milgrom–Weber existence theorem
for Bayesian games with uncountable type
spaces~\citep{MilgromWeber1985}, infinite-horizon discounted
stochastic games~\citep{Shapley1953stochastic, MertensNeyman1981},
and continuous-action or public-randomization variants of the folk
theorem.  The current library proves the discrete observable
mixed-action approximate discounted folk theorem of
\Cref{thm:folk-discounted}; a measure-theoretic extension would
give it continuous companions.

This is a substantial extension and would change the library's
character.  The fixed-point ingredient is partly isolated:
\TT{Math/SchauderFixedPoint.lean} proves Schauder's theorem for
compact convex subsets of real normed spaces.  What remains for
continuous games is not just a fixed-point theorem but the
measure-theoretic and topological game layer around it.  We see
that less as a single project and more as a parallel library with
shared infrastructure (the
\TT{KernelGame}/\TT{GameForm} skeleton generalizes to a kernel
$\K : \prod_i \Strat_i \to \mathcal{P}(\Outcome)$ for a measure
type $\mathcal{P}$, with the discrete \TT{PMF} as one
instantiation).

\subsection{Cooperative game theory}
\label{sec:future:cooperative}

The cooperative branch lives at \TT{Cooperative/} (a parallel
paradigm to the non-cooperative core occupying the rest of the
library; see \S\ref{sec:theorems:shapley-uniqueness} for the
framing).  Already formalized:\ TU coalitional games with the
Shapley value~\citep{Shapley1953} and all four classical axioms,
the unanimity-basis decomposition (Möbius inversion on the subset
lattice), the full Shapley uniqueness theorem
(\Cref{thm:shapley-unique}), the Banzhaf~\citep{Banzhaf1965} and
Shapley–Shubik~\citep{ShapleyShubik1954} power indices, simple
(voting) games, convex (supermodular) games with the
$\IsConvex \Leftrightarrow$ monotone-marginals characterization
\citep{Shapley1971} and closure under sum and nonnegative scalar,
the core (efficient $\land$ coalition-rational) with the
convex-set closure property and individual rationality, additive
games (the identity allocation), and the 3-player majority game
as a worked example.  Nash bargaining
\citep{Nash1950bargaining} is formalized through the IR/Pareto
characterization, with symmetric and affine-invariant variants;
the \emph{egalitarian} bargaining solution (Kalai 1977) is also
formalized as \TT{IsEgalitarian} with the equal-gain accessor and
the agreement-with-Nash-on-symmetric-problems sanity check.
Stable matching~\citep{GaleShapley1962} is formalized through
\TT{IsMatching}/\TT{IsBlockingPair}/\TT{IsStable} predicates and
structural lemmas.

Natural extensions:\ Bondareva–Shapley balanced collections
\citep{Bondareva1963, Shapley1967} characterizing core-nonempty
games (a flagship LP-duality result); the nucleolus
\citep{Schmeidler1969}; the Aumann–Shapley value for non-atomic
games~\citep{AumannShapley1974}; NTU coalitional games; Shapley's
1971 theorem that convex games have nonempty cores (and the
Shapley value is in the core); Kalai–Smorodinsky
\citep{KalaiSmorodinsky1975} and other bargaining solutions; the
Gale–Shapley deferred-acceptance algorithm to construct a stable
matching from arbitrary preferences.

\subsection{Information design and signaling}
\label{sec:future:info-design}

In \emph{Bayesian persuasion}~\citep{KamenicaGentzkow2011} a
sender designs an information structure (a signal-generation
mechanism that maps the state of the world to a public message)
to influence a receiver's posterior beliefs and hence their
action; the design problem is to choose the most persuasive
signal mechanism subject to the receiver's Bayesian rationality.
\emph{Signaling games}~\citep{Spence1973} are the strategic
analogue with an informed sender choosing a costly signal whose
cost may itself depend on type.  \emph{Information
design}~\citep{Bergemann2019} generalizes the persuasion setup to
multiple receivers and richer outcome rules.  All three sit on
top of the Bayesian-game infrastructure of
\S\ref{sec:mech:bayesian} and would benefit from a continuous-type
extension, but admit interesting finite-grid formalizations
directly.

\subsection{Social choice impossibility theorems}
\label{sec:future:social-choice}

\emph{Arrow's impossibility theorem}~\citep{Arrow1951} says no
social-welfare function aggregating individual ordinal preferences
over $\ge 3$ alternatives can simultaneously satisfy unanimity,
non-dictatorship, and independence of irrelevant alternatives.
\emph{Gibbard–Satterthwaite} \citep{Gibbard1973, Satterthwaite1975}
is the strategic analogue:\ any non-dictatorial social choice
function with full range over $\ge 3$ alternatives is
manipulable.  \emph{Sen's liberal paradox}~\citep{Sen1970} shows
that even a minimal individual-rights condition is inconsistent
with Pareto efficiency plus universal domain.  All three are
statable on the existing social-choice setup, the proofs are
combinatorial and do not require probability, and they would fit
the library cleanly.

\subsection{Multi-agent learning}
\label{sec:future:learning}

The FOSG and observation-model layers are built precisely so that
multi-agent reinforcement-learning algorithms — \emph{fictitious
play} (each player best-responds to the empirical distribution of
opponents' past actions), self-play, MCTS, regret matching — can
be formalized as strategy-update rules on top of an existing
game.  \emph{No-regret learning} is the central convergence
notion:\ an algorithm has \emph{vanishing average regret} when
its average per-round payoff approaches that of the best fixed
action in hindsight; the classical theorems
\citep{Cesa-BianchiLugosi2006, BlumMansour2007} link no-regret
play of a repeated game to convergence to CCE (external regret)
or CE (internal regret).  These are the natural formal targets;
the strategic-form definitions they need are already in place.

\subsection{Stable matching and Gale–Shapley}
\label{sec:future:matching}

The library's \TT{Cooperative/Matching.lean} formalizes the
matching predicates (\TT{IsMatching}, \TT{IsBlockingPair},
\TT{IsStable}) and a few structural lemmas, but not the
Gale–Shapley deferred-acceptance algorithm itself nor the
existence of a stable matching from an arbitrary preference
profile~\citep{GaleShapley1962}.  The algorithm is constructive,
terminates in $O(n^2)$ steps, and is a natural target for a Lean
implementation paired with a correctness proof.  Bertot's Coq
formalization \citep{Bertot2016} is a useful reference point.

\subsection{Symmetric Nash existence}
\label{sec:future:symmetric-nash}

Existence of a \emph{symmetric} mixed Nash equilibrium in a
finite symmetric game~\citep{Nash1951} is a classical corollary of
mixed Nash existence (\Cref{thm:nash-mixed}) by restricting the
gain map to the symmetric subspace of the product simplex.  The
restriction step is straightforward but is not packaged on top
of \TT{SymmetricGame.lean}.

\subsection{Type-theoretic refactoring opportunities}
\label{sec:future:refactor}

We close with two design directions internal to the library
itself.  First, an open-games-style
reformulation~\citep{GhaniHedgesWinschelZahn2018} would expose the
\TT{KernelGame} category in a shape suitable for compositional
reasoning at a higher abstraction level; this would not change
the theorems but might simplify their proofs.  Second, the
library's \TT{noncomputable} discipline could be tightened by
isolating the constructive fragment (definitions and theorems
that do not invoke classical reasoning) as a separately-named
namespace; this would make the boundary between the constructive
finite-game fragment and the non-constructive existence-of-Nash
fragment visible in user code.
